---
title: "p8105_hw3_db3180"
author: "Divya Bisht"
date: "10/9/2018"
output: github_document
---

## Problem 1 
Uploading problem 1 dataset
```{r setup, include=FALSE}
install.packages("devtools")
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
brfss_data = brfss_smart2010 %>%
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  mutate(response = factor(response, levels = c("Excellent",  "Very good", "Good", "Fair", "Poor")))
```

##Problem 2
```{r}
instacart_data = instacart %>%
  janitor::clean_names()
```
This dataset has 1384617 rows/observations and 15 columns/variables. Some key variables include: product_id, reordered (which tells us if the product had been reordered by a customer), order_hour_of_day, aisle, department, etc. 



```{r}
aisle = nrow(distinct(instacart_data, aisle))
```
There are `r aisle` aisles. 
```{r}
aisle_most = aisle %>%
  count(product_id) %>%
  arrange(desc(n))
```
The aisle that most of the products are ordered from: (need to count which products are ordered the most)

##Problem 3
```{r}
ny_noaa_data = ny_noaa %>% 
  janitor::clean_names()
```
This data has 2595176 rows/observations and 7 columns/variables. Some key variables are: id(weather stattion ID, date (date of observation), prcp (Precipitation (tenths of mm), snow (Snowfall (mm)), and tmax and tmin (max and minimum temperatures). 

